\documentclass[journal]{IEEEtran}
\usepackage[utf8]{inputenc}

\usepackage{graphicx}
%\usepackage[caption=false,font=footnotesize]{subfig}

\usepackage{url}
% Making the references and links clickable
\usepackage{hyperref}
\hypersetup{
	%colorlinks=false,
	pdfborder={0 0 0}
}

\usepackage{xcolor}
\newcommand{\toDo}[1]{\textcolor{red}{#1}}

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{University of Brasília}
\rhead{\thepage}
\cfoot{Comparing the Performance of Finite-State Machines with Different Numbers of States on TORCS}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\begin{document}
	\title{Comparing the Performance of\\Finite-State Machines with\\Different Numbers of States on TORCS}
	
	\author{\IEEEauthorblockN{Bruno H. F. Macedo\IEEEauthorrefmark{1},
			Gabriel F. P. Araujo\IEEEauthorrefmark{1},
			Gabriel S. Silva\IEEEauthorrefmark{1},\\
			Matheus C. Crestani\IEEEauthorrefmark{1},
			Yuri B. Galli\IEEEauthorrefmark{1} and
			Guilherme N. Ramos\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}\\[0.2cm]}
		\IEEEauthorblockA{\IEEEauthorrefmark{1}University of Brasília}
		\IEEEauthorblockA{\IEEEauthorrefmark{2}gnramos@unb.br}}
	
	\maketitle
	
	\begin{abstract}
		
		This work presents two different approaches developed to control a self-driving car in the racing environment
		simulated by TORCS. The problematic revolves around the representation of the complex behaviour that
		describes a pilot during a race, whose proposed solution is a finite-state machine. \toDo{Reduzir}The first method models
		the problem with states that separate the full driving behaviour into smaller fragments, thus simplifying the
		analysis and permitting parallel optimization; whilst the second method reduces the number of states with the
		objective of improving the performance, which is done by attenuating the impact that the function that
		manages the transition between states has on the controller as a whole. Furthermore, in order for the final
		controller to attain competitive status, i.e. parameter fine tuning, the incorporation of a genetic algorithm
		was performed. Evolving the driver using this method initially required the definition of a set of parameters
		to be the target of optimization, which would constitute the search space of the 
		
		
		Evolving the driver using Genetic Algorithm passed by defining the set of parameters 
		which would be the target to be optimazed, it initializion, random attributes insertion, evaluetion fuction 
		which provide a score, value that determine how good the parameters is.\toDo{Falar como foi, sucintamente,
		o processo de evolução com o Algoritmo Genético(é o suficiente?)}
		Validation\toDo{evaluetion?} occurred through exhaustively testing the configurations of the two approaches, comparing them
		along with artificial intelligences provided by the platform and also State of the Art implementations.
				
	\end{abstract}
	
	\begin{IEEEkeywords}
		
		finite state machines, computer games, TORCS, artificial intelligence, genetic algorithms, self-driving car
		\toDo{Finish keywords}
		
	\end{IEEEkeywords}
	
	\section{Topics}%
	
		Talk about:
		
		\begin{itemize}
			\item How the problem appeared;
			\item The approach chosen to solve it;
			\item How we evolved it by applying a genetic algorithm;
			\item How we improved the process of evolving through virus infection.
		\end{itemize}
		
		Include:
		\begin{itemize}
			\item State-of-art exposure;
			\item Model definition (theoretical outline);
			\item Test results;
			\item Results analysis;
			\item Prospects;
			\item Future works.
		\end{itemize}
		\newpage
	
	\input{Introduction}
	\input{TORCS_Environment}
	\input{Related_Works}
	\input{FSMDriver_ControllerStructure}
	\input{Genetic_Algorithm}
	\input{Methodology_Experiments}
	\input{Analysis_Conclusion}
	\input{Future_Works}
	
	%\nocite{*}
	\bibliographystyle{IEEEtran}
	\bibliography{Bibliography}
	\toDo{Adequar as referências ao padrão do IEEE: \url{http://www.ieee.org/documents/ieeecitationref.pdf}. Quando
	há 3 ou mais autores colocar et al.}
	
	
	
\end{document}
