\section{\textbf{FSMDriver - Controller Structure}} \label{sec:fsm}

	\subsection{First Approach - A Finite-State Machine With Five States}
	
	According to Mat Buckland in \emph{Programming Game AI By Example}~\cite{AI}:
	
	\begin{quotation}
		
		\emph{
		``A finite state machine is a device, or a model of a device, which has a finite number of states it can be in
		at any given time and can operate on input to either make transitions from one state to another or to cause
		an output or action to take place. A finite state machine can only be in one state at any moment in time.''}
		
	\end{quotation}
	
	Some of the main aspects desired to idealize a controller for TORCS were sufficed by the concept of	finite state
	machines~\cite{FSM}, the most important one being the goal of reaching an autonomous driving behaviour in a car
	race. This architecture was chosen in order to transform the problem of complex driving into smaller problems of
	situations found within the racing environment. Initially, the design of the finite-state machine proposed
	comprised the following states:
	
	\begin{itemize}

	\item \emph{Straight Line};
	\item \emph{Approaching Curve};
	\item \emph{Curve};
	\item \emph{Out of Track};
	\item \emph{Stuck}.

	\end{itemize}
	
	Essentially, for this method, normal behaviour covered \emph{Straight Line}, \emph{Approaching Curve} and
	\emph{Curve}, as the controller was located inside the track boundaries and no recovery actions needed to be
	considered, whereas exception behaviour consisted of \emph{Out of Track} and \emph{Stuck}, situations in which
	such conduct was expected. Here, a consideration needs to be taken into account: the real first model of the
	finite-state machine did not have an \emph{Approaching Curve} state, but, as the interpretations of the demeanour
	concerning the \emph{Straight Line} and the \emph{Curve} were so different from one another, a preparation had to
	be established so as to smoothen the transitions between them.
	
	If the controller was currently in \emph{Straight Line}, it would be expected of him to simply go as fast as he
	could, with no steering changes whatsoever; when in \emph{Approaching Curve} state, he would reposition himself
	in relation to the track and recalibrate his speed in order to make better curves; or, when in situations of
	\emph{Curve}, the pilot would reduce speed proportionally to the curvature of the curve, and then redirect
	himself towards the sensor pointing the biggest distance value read - which represents the direction of the curve.
	For the exception states, even though the expected deportment is well known, e.g. a stuck controller should
	maneuver the car out of the current situation and proceed to normal race conduct, the implementations vary among
	developers. The strategy chosen for the exception states was used on both proposals as a matter of regularity of
	comparison, and is explained on the next subsection.
	
	The major problem about this way of treating the matter is that the function responsible for choosing which state
	is more appropriate for each situation would more than often be overcharged, and, in some cases, rather different
	sets of parameters received by it would result in the same classification among the states. Thus, in order to
	minimize the dependency of the driving performance in relation to the function in charge of the transition
	between states, a project decision was made to reduce the number of states.
		
	\subsection{Proposition - A Finite-State Machine With Three States}
	
	The very nature of the initial architecture gave rise to the new approach. As mentioned within this very section,
	three of the states were innately part of a common bigger state, thereby \emph{Straight Line},
	\emph{Approaching Curve} and \emph{Curve} summed into \emph{Inside the Track}, resulting in the new controller
	with only three states, which were:
	
	\begin{itemize}
		
		\item \emph{Inside the Track};
		\item \emph{Out of Track};
		\item \emph{Stuck}.
		
	\end{itemize}
	
	\emph{Inside the Track}, therefore, is how the car, desirably, will spend most part of the time. The controller
	assumes a position of increasing the speed while steering towards the sensor with the biggest read value. This
	state also brakes, if necessary, when approaching turns.
	
	\emph{Out of Track} is when, for any unknown reason, the car is found outside of the track limits. In this case,
	the proper behaviour is to try to return to the lane. In road tracks, the outside track normally has a different
	terrain, sometimes dirt-based, meaning that skidding frequently occurs, and in a effort to avoid this, a control
	system to brake when the car begins skidding above a threshold was implemented.
	
	\emph{Stuck} represents any given situation that the car is unable to progress in the race. This is a delicate
	state, because it presents itself as difficult to identify and also due to its impact to the performance of the
	controller. In order to detect \emph{Stuck} circumstances, the speed of the car is monitored throughout the race,
	during every game tick, if it lingers with a low speed for a determined period, then it is considered stranded,
	or stuck. When detected, this state activates the reverse gear of the car and turns it until its front is
	directed towards the correct axis of the track. The reason why \emph{Stuck} is a sensitive state is because, when
	detected early, might indicate false positive, and when detected late, could lessen the efficiency of the
	controller. Thusly, detecting \textit{Stuck} situations is crucial, and so is handling the car out of them.
	
	In conclusion, each state in this manner of dealing with the process becomes, ideally, an independent problem,
	whose solution can be attacked separately. This way, they can all have individual sets of parameters susceptible
	to improvement, which will be discussed in the next section.